\documentclass{resume}

\usepackage{hyperref}
\renewcommand{\categoryfont}{\sc}
%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\addtolength{\textwidth}{-2\oddsidemargin}
\addtolength{\textwidth}{\marginparwidth}
\addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\bullet$}
\renewcommand{\labelitemi}{$\circ$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Amin Khorsandi}
% ------ Title  -----------------------------------------------------

\address{Blomgatan 20\\
	 16960 Solna\\
	 Sweden\\}
        {+46766344669 (mobile)\\
	\mbox{\small\tt aminkhorsandi@gmail.com}\\
	\mbox{\small\tt \url{https://se.linkedin.com/in/aminkhorsandi}}}

\begin{document}
\maketitle

\begin{center}
\line(1,0){400}
\end{center}

% ------ Summary  ----------------------------------------------------
\par \begin{flushleft}A passionate and highly motivated software developer 
and test engineer with deep interest and extensive experiences in the 
fields of large scale software design and development, test driven 
development, test design and test automation from theoretical point 
of view as well as their real-world applications in industry and life.
\end{flushleft}

\begin{center}
\line(1,0){400}
\end{center}

% ------- Skills ------------------------------------------------------
\begin{category}{Technical competence}
\citem {Programming languages:}\hspace{1 mm}Object Oriented Programming 
(\texttt{Java Standard Edition}, \texttt{Java Enterprise Edition}, \texttt{C++}), 
Functional Programming (\texttt{Erlang}, \texttt{StandardML}), 
shell scripting (\texttt{Bash} and \texttt{tcsh}), \texttt{C}, \texttt{Python}, 
and \texttt{Groovy};

\citem {Web technologies:}\hspace{1 mm}\texttt{JavaScript}, \texttt{JQuery}, \texttt{JSF} 
\texttt{MVC}, \texttt{PHP}, \texttt{CSS}, \texttt{Web Services}, \texttt{RESTful}, \texttt{ASP.Net};

\citem {Database technologies:}\hspace{1 mm}\texttt{Oracle}, \texttt{MySQL}, \texttt{Microsoft SQL Server} 
, \texttt{Erlang Mnesia} (A distributed telecommunications DBMS), \texttt{Hibernate ORM} and \texttt{NHibernate};

\citem{Automated testing and verification:}\hspace{1 mm}in-depth knowledge of unit and integration 
testing using XUnit family of frameworks such as \texttt{JUnit}, \texttt{TestNG}, \texttt{NUnit} 
and \texttt{EUnit}; familiar with feature testing concept and tools like \texttt{Erlang} common-test 
framework and \texttt{Java JCAT}; very well experienced in system and acceptance testing techniques;

\citem {Other:}\hspace{1 mm}immense experiences and understanding of Cloud and Virtualization technologies, 
Continues Integration and delivery (\texttt{Jenkins}, \texttt{TeamCity}), 
web application servers (\texttt{Tomcat}, \texttt{WildFly}), 
MVC frameworks (\texttt{Spring}, \texttt{Django}, \texttt{ASP.NET MVC}, \texttt{Node.js}), 
build automation tools (\texttt{Maven}, \texttt{Apache Ant}, \texttt{GNU make}), Linux (workstation/cluster), 
Linux programming interface, parallel and concurrent programming and internet protocol suite.
Excellent troubleshooting and problem solving skills.

\end{category}

\begin{center}
\line(1,0){400}
\end{center}

% -------- Work experience --------------------------------------------
\begin{category}{Work \\experience}

\citem{R\&D Software Developer/test engineer}, Ericsson, Stockholm, Sweden (November 2012 - Now)\\
Working in a cross functional team for SBG product in CBA migration project to 
transfer and extend the existing product code base into the new architecture and also 
adding new features and functionality to the system to support the customer's requirements.
Using TDD and pair programming techniques and Agile way of work to improve code quality and
speed up team's assignments. Applying Continuous Integration practices via automated build and tests to 
make sure the high quality software will be delivered to the market and on time.
\begin{itemize}
 \item Design and implement features for the SBG software system from scratch using 
       Erlang and OTP design patterns.
 \item Implement unit tests for the new modules and functions of the system as well as 
       writing the integration test to test modules combined and grouped together. 
 \item Extending and improving existing features of the system to facilitate the 
       migration into the new architecture.
 \item Design and implement feature test suites to test different features of the 
       system such as robustness, software management, logging, network, registration 
       etc. using Erlang common test framework.
 \item Automate the build and test process of the whole product in order to reduce the production time
       while securing delivery of the high quality software.
 \item Make use of container technologies (\texttt{LXC}) and Kernel Based Virtualization in order to utilize the 
       available test hardware in a much more efficient and cost saving way.
\end{itemize}

\citem{Research Assistant}, Mobility Research Group, Department of Information Technology, 
Uppsala University, Uppsala, Sweden (July 2012 - October 2012)\\
Continue to work on my thesis and extend the features of the type checker which I 
implement during my master thesis work.
\begin{itemize}
 \item Study the theory of type systems and mobile processes with a 
       focus on the typed Psi-calculi theory and its implementation details.
 \item Implement and extend the type system for different instances of Psi-calculi 
       using the Standard ML programming language.
\end{itemize}

\citem{Software Developer}, Tehran Water Company, Tehran, Iran (May 2005 - August 2009)\\
Working as a software developer for the Tehran Water Telemetry project. The aim of the 
project is to implement the telemetry and telecommand software system for the company.
\begin{itemize}
 \item Design, develop and maintain the telemetry software system on the main control center using 
       \texttt{C++} (real time core parts) and on the analyzing and visualization part in \texttt{Java}.
 \item Design, develop and maintain the software system on the remote control stations using \texttt{C\#})
       on Microsoft Windows Server platform.
 \item Design and implement the database system of the telemetry software 
       using Oracle database management system.
 \item Write unit test using \texttt{NUnit}, \texttt{JUnit} and function test 
       suites to execute load, performance and stress tests (using \texttt{Apache JMeter}) 
       to make sure the highest quality of software system. 
\end{itemize}

\citem{Front-end and Back-end Developer (part-time)}, SCWMRI Research Institute, 
Tehran, Iran (April 2007 - September 2008)
\begin{itemize} 
\item Design and develop a CMS (content management system) to represent as a 
      digital portal for the institute using \texttt{ASP.NET MVC}.
\item Design the database management system for data manipulation of the CMS using \texttt{MS-SQL}.
\end{itemize}

\end{category}

\begin{center}
\line(1,0){400}
\end{center}

% ------- Education ---------------------------------------------------
\begin{category}{Education}
\citem{Uppsala University}, Uppsala, Sweden. \\
Diploma [M.Sc.] in computer science, (grades: 87\%).\\
Thesis title: {\em Implementing typed Psi-Calculi.}\\
Key courses: Large scale programming, Verification methods, Data mining, 
From domains to requirements, Test methodology,
Software architecture with Java, Parallel programming, Compiler design project. 
\citem{Tabriz University}, Tabriz, Iran.\\
Diploma [B.Sc.] in computer science (software engineering option), May 2004.\\
Key courses: Information system analysis and design, Computer networks, 
Management information systems, Algorithm design and analysis, Database technology.

\end{category}

\end{document}
